Analysing Constraint Grammar with a SAT solver

### 2015-10-21 paper/lrec/eval_futurework.tex
stuff

\todo{Other things we found from the grammar:}
With the Spanish grammar, the method pointed us to a nonsensical set definition.
\texttt{w2<n><np><adj><det><preadv><adv><vblex><vbmod><vbhaver><vbser><prn><pr><cnjcoo><cnjsub><cnjadv><rel><ij>}

For future work, we want to improve the performance and scale up to larger grammars, and handle the full expressivity of CG-3, with \textsc{map}, \textsc{add} and \textsc{substitute} rules.
We want to also ask different questions, such as \todo{...}.
Finally, we want to test the approach to other grammar formalisms.

>>>>

% Instead of whole grammar, look at specific rules, test with different number of rules before

\todo{Analyse the results. I didn't even touch the Finnish results yet. Maybe mention other things we found from the grammar, like the nonsensical set definition from Spanish grammar (confused and and or, requiring a word to be noun AND verb AND conj AND preposition ...). }

Currently, the speed is not great. The Finnish grammar approaches a realistic size of grammars.
The size of the SAT problem was \todo{some real numbers and analysis here \& promises that it can be fixed}.

% w2<n><np><adj><det><preadv><adv><vblex><vbmod><vbhaver><vbser><prn><pr><cnjcoo><cnjsub><cnjadv><rel><ij>

For future work, we want to improve the performance and scale up to larger grammars, and handle the full expressivity of CG-3, with \textsc{map}, \textsc{add} and \textsc{substitute} rules.
We want to also ask different questions, such as \todo{...}.
We can be smarter about SAT things.

Compare with a corpus-based test: do we find the same problems?

Finally, we want to test the approach to other grammar formalisms.
